Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-06-21 paper/main.tex

@@

\subsubsection{Configuring and querying Davos}\label{subsec:config}

Davos's behavior may be customized by modifying a set of attributes attached to
the \texttt{davos} module object that is added to the workspace when Davos is
imported. These attributes may be modified, displayed, or checked
programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
illustrative example or Sec.~\ref{subsec:implementation} for implementation
details and additional information). These include:

\item \texttt{.suppress\_stdout}: If this attribute is set to
  \texttt{True} (default: \texttt{False}), Davos suppresses
  printed (console) outputs from both itself and the installer program.
  This can be useful when smuggling packages that need to install many
  dependencies and/or generate extensive output. However, if the installer
  program throws an error, both its stdout and stderr streams will be
  displayed alongside the Python traceback to allow for debugging.

\item \texttt{.project}: This attribute is a string that specifies the name of
the ``project'' associated with the current notebook. As described in
Section~\ref{subsec:projects}, a notebook's project determines where and how
any \textttt{smuggle}d dependencies are installed if they are not available in
the current runtime environment. By default, this attribute is named according
to the current notebook's absolute file path. However, the project name may be
customized to enable shared dependency installations across notebooks (see
Sec.~\ref{subsec:projects}).

\end{itemize}

\noindent Davos namespace also defines the \texttt{davos.configure()} function,
which allows setting multiple configuration options simultaneously. In addition
to the above configurable attributes, the \texttt{davos} object also includes
several read-only attributes that contain potentially useful information about
the current environment or Davos's behavior:

\begin{itemize}

\item \texttt{.environment}: This attribute's value is a string describing the notebook
environment Davos was imported into. As of the current version (0.2.0), this
attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”}.

  \item \texttt{.ipython\_shell}: This attribute contains the global IPython \texttt{InteractiveShell} instance underlying the notebook kernel session.

  \item \texttt{.smuggled}: This attribute is set to a Python dictionary that functions as a cache of any \texttt{smuggle} commands run during the current
session.  The dictionary's keys are package names and the values are arguments passed via the corresponding smuggle statement's onion comment.

  \item \texttt{.all\_projects}: This attribute contains a list of all local projects (i.e., projects with virtual environment directories located in \texttt{\$HOME/.davos/projects}).  See Section~\ref{subsec:projects} for additional information about Davos projects.

\end{itemize}

>>>>

\subsubsection{The Davos config object}\label{subsec:config}

The Davos config object provides a high-level interface for
controlling various aspects of Davos's behavior. After
importing Davos, the \texttt{davos.con\-fig} object (a
singleton) exposes configurable options as attributes that can be
modified, displayed in the notebook, or checked programmatically at runtime
(see Sec.~\ref{sec:illustrative-example} for an illustrative example or
Sec.~\ref{subsec:implementation} for implementation details and
additional information). These include:

\item \texttt{.suppress\_stdout}: If this attribute is set to
  \texttt{True} (default: \texttt{False}), Davos suppresses
  printed (console) outputs from both itself and the installer program.
  This can be useful when smuggling packages that need to install many
  dependencies and/or generate extensive output. However, if the installer
  program throws an error, both its stdout and stderr streams will be
  displayed alongside the Python traceback to allow for debugging.
\end{itemize}

\noindent The top-level Davos namespace also defines
convenience functions for setting and checking whether Davos
is active (\texttt{davos.activate()}; \texttt{davos.deactivate()};
\texttt{davos.is\_active()}) as well as the \texttt{davos.configure()}
function, which allows setting multiple configuration options
simultaneously.

@@
